---
title: "Coursera-Developing Data Products-Shinyapps Reproducible Pitch Presentation "
author: "Swarup Kumar Roy"
date: "`r Sys.Date()`"
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Slide 1: MPG Efficiency Explorer
MPG Efficiency Explorer is a simple presentation about predicting fuel efficiency using vehicle data.

This project shows how a few car features can help estimate miles per gallon in a clear and practical way.

## Slide 2: The Fuel Efficiency Problem
With fluctuating gas prices, understanding vehicle efficiency is important for both consumers and manufacturers.

Weight is often the enemy of efficiency, and engine size can also have a strong impact on fuel consumption.

Our app gives an instant, data-driven prediction so users can estimate MPG without doing manual calculations.

## Slide 3: Data-Driven Foundations
The application is built on the classic `mtcars` dataset, which contains measurements for 32 automobiles.

We use a small set of important variables, especially `mpg`, `wt`, and `cyl`, because they are useful for prediction.

```{r}
summary(mtcars[, c("mpg", "wt", "cyl")])
fit <- lm(mpg ~ wt + cyl, data = mtcars)
coef(summary(fit))
```

## Slide 4: App Features
The MPG Efficiency Explorer is designed to be simple and interactive.

It includes user-friendly sliders and buttons, visual feedback, and a quick comparison against the dataset.

The model is based on standard statistical methods, so the results are easy to explain and understand.

## Slide 5: Links and Hosting
- Launch the Shiny App at [https://swarup-jhu.shinyapps.io/Coursera-Data-Product-Shiny-App/]
- View Source Code on GitHub [https://github.com/swarup-jhu/Data-Products-Shiny-Application].
-
-
-
Thank You

